Best Practices for Alchemical Free Energy Calculations [Article v\versionnumber]

### 2020-12-23 paper/manuscript.tex
Updated for publication.
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,bestpractices]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Please note that these options may affect formatting.

@@

\newcommand{\versionnumber}{1.0} % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/alchemistry/alchemical-best-practices}} %this should be the main github repository for this article
\newcommand{\expect}[1]{\left\langle{#1}\right\rangle}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Best Practices for Alchemical Free Energy Calculations [Article v \versionnumber]}
\author[1*]{Antonia S. J. S. Mey}
\author[2]{Bryce K. Allen}
\author[3]{Hannah E. Bruce Macdonald}
\author[3*]{John D. Chodera}
\author[9]{David F. Hahn}
\author[1,10]{Maximilian Kuhn}
\author[1]{Julien Michel}
\author[4*]{David L. Mobley}
\author[5]{Levi N. Naden}
\author[6]{Samarjeet Prasad}
\author[2,7]{Andrea Rizzi}
\author[1]{Jenke Scheen}
\author[8*]{Michael R. Shirts}
\author[9]{Gary Tresadern}
\author[2]{Huafeng Xu}
%
\affil[1]{EaStCHEM School of Chemistry, David Brewster Road, Joseph Black Building, The King's Buildings, Edinburgh, EH9 3FJ, UK}
\affil[2]{Silicon Therapeutics, Boston, MA, USA}
\affil[3]{Computational and Systems Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York NY, USA}
\affil[4]{Departments of Pharmaceutical Sciences and Chemistry, University of California, Irvine, USA}
\affil[5]{Molecular Sciences Software Institute, Blacksburg VA, USA}
\affil[6]{National Institutes of Health, Bethesda, MD, USA}
\affil[7]{Tri-Institutional Training Program in Computational Biology and Medicine, New York, NY, USA}
\affil[8]{University of Colorado Boulder, Boulder, CO, USA}
\affil[9]{Computational Chemistry, Janssen Research \& Development, Turnhoutseweg 30, Beerse B-2340,Belgium}
\affil[10]{Cresset, Cambridgeshire, UK}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PUBLICATION INFORMATION
%%% Fill out these parameters when available
%%% These are used when the "pubversion" option is invoked
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pubDOI{10.XXXX/YYYYYYY}
\pubvolume{<volume>}
\pubyear{<year>}
\articlenum{<number>}
\datereceived{Month, Day, Year}
\dateaccepted{Month, Day, Year}

@@

Let
$K_C$ be the equilibrium constant between DFG-in and DFG-out
conformations of one kinase, and $K_D^\ast$ be the dissociation
constant of a type II inhibitor against this kinase, the apparent
binding constant of this inhibitor against this kinase is then
\begin{equation}
  K_b = K_D^\ast \frac{1 + K_C}{K_C}
  \label{eqn:conformational-binding}
\end{equation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,bestpractices,ASAPversion]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Please note that these options may affect formatting.

@@

\newcommand{\versionnumber}{0.3} % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/alchemistry/alchemical-best-practices}} %this should be the main github repository for this article
\newcommand{\expect}[1]{\left\langle{#1}\right\rangle}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Best Practices for Alchemical Free Energy Calculations [Article v\versionnumber]}
\author[1*]{Antonia S. J. S. Mey}
\author[2]{Bryce K. Allen}
\author[3]{Hannah E. Bruce Macdonald}
\author[3*]{John D. Chodera}
\author[9]{David F. Hahn}
\author[1,10]{Maximilian Kuhn}
\author[1]{Julien Michel}
\author[4*]{David L. Mobley}
\author[5]{Levi N. Naden}
\author[6]{Samarjeet Prasad}
\author[2,7]{Andrea Rizzi}
\author[1]{Jenke Scheen}
\author[8*]{Michael R. Shirts}
\author[9]{Gary Tresadern}
\author[2]{Huafeng Xu}
%
\affil[1]{EaStCHEM School of Chemistry, David Brewster Road, Joseph Black Building, The King's Buildings, Edinburgh, EH9 3FJ, UK}
\affil[2]{Silicon Therapeutics, Boston, MA, USA}
\affil[3]{Computational and Systems Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York NY, USA}
\affil[4]{Departments of Pharmaceutical Sciences and Chemistry, University of California, Irvine, USA}
\affil[5]{Molecular Sciences Software Institute, Blacksburg VA, USA}
\affil[6]{National Institutes of Health, Bethesda, MD, USA}
\affil[7]{Tri-Institutional Training Program in Computational Biology and Medicine, New York, NY, USA}
\affil[8]{University of Colorado Boulder, Boulder, CO, USA}
\affil[9]{Computational Chemistry, Janssen Research \& Development, Turnhoutseweg 30, Beerse B-2340,Belgium}
\affil[10]{Cresset, Cambridgeshire, UK}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PUBLICATION INFORMATION
%%% Fill out these parameters when available
%%% These are used when the "pubversion" option is invoked
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pubDOI{10.33011/livecoms.2.1.18378}
\pubvolume{2}
\pubyear{2020}
\articlenum{18378}
\datereceived{5 August 2020}
\dateaccepted{25 November 2020}

@@

Let
$K_C$ be the equilibrium constant between DFG-in and DFG-out
conformations of one kinase, and $K_D^\ast$ be the dissociation
constant of a type II inhibitor against this kinase, the apparent
binding constant of this inhibitor against this kinase is then
\begin{equation}
  K_D = K_D^\ast \frac{1 + K_C}{K_C}
  \label{eqn:conformational-binding}
\end{equation}
